Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-25 docs/manuscript/manuscript.tex
Updates from Overleaf

% {\reversemarginpar\marginnote{\scriptsize\rd The introduction should end with a paragraph summarizing the contents and layout of the remainder of the manuscript. E.g. ``In the next section we discuss relevant prior research on water accessibility quantification. Next, we present the data and methods...''}} 
In this paper, we investigate further on what
variables should be included to enhance the accessibility of improved drinking water.
In the next section we discuss relevant prior research on water accessibility quantification. We are interested in what type of modes of
transportation are utilized to provide clean and drinking water to the community. Also, our objective is to investigate
the time it takes to transport water to the community in a global modeling context. So that we can develop and quantify
water accessibility in different countries to compare different trends. Also, we will be exploring the most efficient
and effective modes of transportation of accessible water. Therefore, the new models will be able to influence and
encourage policymakers in specific countries to improve water accessibility for all. Next we present the data and methods of approaching the quantification of the water accessibility.

\section{Relevant work}

\citet{jagals2006does} highlights in a case study in rural area in South Africa discovered providing small
communities, using untreated river water as their water source, with good quality water with a piped distribution system
and increase of accessibility by installing communal taps did not fall within parameters of safe water. Their research
gives a potential understanding even making the drinking water accessible might not improve the quality of the water
itself.

>>>>

% {\reversemarginpar\marginnote{\scriptsize\rd The introduction should end with a paragraph summarizing the contents and layout of the remainder of the manuscript. E.g. ``In the next section we discuss relevant prior research on water accessibility quantification. Next, we present the data and methods...''}} 
\section{Objectives}
In this paper, we investigate further on what
variables should be included to enhance the accessibility of improved drinking water.
In the next section, we discuss relevant prior research on water accessibility quantification. We are interested in what type of modes of
transportation are utilized to provide clean and drinking water to the community. Also, our objective is to investigate
the time it takes to transport water to the community in a global modeling context. So that we can develop and quantify
water accessibility in different countries to compare different trends. Also, we will be exploring the most efficient
and effective modes of transportation of accessible water. Therefore, the new models will be able to influence and
encourage policymakers in specific countries to improve water accessibility for all. Next, we present the data and methods of approaching the quantification of the water accessibility.

\section{Contribution}

\citet{jagals2006does} highlights in a case study in a rural area in South Africa discovered providing small communities. The rural area used untreated river water as their water source. The Researchers installed good quality water with a piped distribution system and increase accessibility by installing communal taps. However, this implementation did not fall within the parameters of safe water. This didn't increase household quantities, which remained around 18 L per person per day. Their research
gives a potential understanding even making the drinking water accessible might not improve the quality of the water
itself.
